---
title: "Basic statistics assignment"
author: "Eric Anjeo"
date: "10/11/2020"
always_allow_html: true
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = F,warning = F)
```


####  [Link](https://github.com/Museve/p8105_hw1_eriq21)

### ***Problem 0.1***
   + random sample of size 10 from a standard Normal distribution
```{r}
set.seed(1234)#for producing same results
x=rnorm(10);
x
```

### ***Problem 0.1***
   + a logical vector indicating whether elements of the sample are greater than 0
```{r}
x>0
```

### ***Problem 0.1***
   + a character vector of length 10
```{r}
chavec=c("one","two","three","four","five","six","seven","eight","nine","ten")
length(chavec)
```
   
### ***Problem 0.1***
   + a a factor vector of length 10, with 3 different factor “levels”
```{r}
facvec=as.factor(c(rep("male",3),rep("female",4),rep("both",3)))
levels(facvec)
```
  
***dataframe***

```{r}
dt=data.frame(x=x,charve=chavec,facvec=facvec)
mean(dt$x)
```
The only mean that we get is for the numeric variable x. The other two (character and factor) generate errors when called.


### ***Problem 2: palmerpenguins***
```{r}
library(dplyr) # data cleaning package
library(corrplot) # for correlation plot
library(GGally) #
library(psych)
data("penguins", package = "palmerpenguins")#reading in the required data
df=penguins#assigning a new name to it
cat("The data has",dim(df)[1],"rows","and",dim(df)[2],"columns")
colnames(df)#it gives the columns names
#Summary stats
summary(penguins)
#plots
psych::pairs.panels(penguins)
```

### we drop empty observations in sex variable
```{r}
penguins <- penguins %>% filter(sex == 'male' | sex == 'female')
summary(penguins)
```

```{r}
penguins %>% group_by(species) %>% tally()
```

```{r}
penguins %>%group_by(species) %>% summarise_if(is.numeric, funs(mean,median)) %>% knitr::kable()
```


### Penguins distributions
```{r}
table(penguins$species, penguins$island)
chisq.test(table(penguins$species, penguins$island)) # meaningful difference
ggplot(penguins, aes(x = island, y = species, color = species)) +
  geom_jitter(size = 3)  +ggtitle('Penguins by Island')
```


